### 2023-03-08 manuscript.tex
Adding manual references and testing fixes [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4366796796

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/83d351133890f19b69d7c2fe2cf608d2bc773ceb/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/83d351133890f19b69d7c2fe2cf608d2bc773ceb}{SORTEE-Github-Hackathon/manuscript@83d3511}
on March 8, 2023.

@@

The use of GitHub has become increasingly popular in recent years due to the expansive GitHub user-community and numerous GitHub resources {[}Perez-Riverol et al. (\protect\hyperlink{ref-kEX5dgzK}{2016}); Bryan (\protect\hyperlink{ref-RVetqmsg}{2018}); \url{https://happygitwithr.com}; \url{https://ourcodingclub.github.io}{]}.
Nevertheless, although multiple articles have encouraged researchers in ecology and evolution to adopt GitHub as part of their research process (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}; \protect\hyperlink{ref-10ghgV3S8}{J. Perkel, 2016}), its use is still not widespread.
Among many other factors, this may be because first-time users without formal training in information technology can face a steep learning curve, as GitHub and its features have been centered on software development (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
Furthermore, there are few domain-specific resources providing tractable examples and practical guidance for researchers in EEB on how to use GitHub {[}but see Kim et al. (\protect\hyperlink{ref-lJAgyhYq}{2022}); \url{https://ourcodingclub.github.io}; \url{https://www.openscapes.org}{]}.
Widespread adoption of GitHub for collaborative research tasks can ultimately enable EEB researchers to save time on creating novel processes for collaboration and focus more on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
More importantly, expanding the availability of data and code management standards, of which GitHub is an increasingly important component, makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).

@@

@@

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/c6a8b5b1c928dbf7ce2eb84352ffbbdf4ff77e1d}{SORTEE-Github-Hackathon/manuscript@c6a8b5b}
on March 8, 2023.

@@

The use of GitHub has become increasingly popular in recent years due to the expansive GitHub user-community and numerous GitHub resources (\protect\hyperlink{ref-RVetqmsg}{Bryan, 2018}; \protect\hyperlink{ref-13jOlVcpp}{\emph{Happy Git with R}, n.d.}; \protect\hyperlink{ref-u5aEVE4B}{\emph{Our Coding Club}, n.d.}; \protect\hyperlink{ref-kEX5dgzK}{Perez-Riverol et al., 2016}).
Nevertheless, although multiple articles have encouraged researchers in ecology and evolution to adopt GitHub as part of their research process (\protect\hyperlink{ref-3DKwn1sY}{Lowndes et al., 2017}; \protect\hyperlink{ref-10ghgV3S8}{J. Perkel, 2016}), its use is still not widespread.
Among many other factors, this may be because first-time users without formal training in information technology can face a steep learning curve, as GitHub and its features have been centered on software development (\protect\hyperlink{ref-139b0pSGc}{Leibzon, 2016}).
Furthermore, there are few domain-specific resources providing tractable examples and practical guidance for researchers in EEB on how to use GitHub (but see \protect\hyperlink{ref-lJAgyhYq}{Kim et al., 2022}; \protect\hyperlink{ref-nDkLlAch}{\emph{Openscapes}, n.d.}, \textgreater; \protect\hyperlink{ref-u5aEVE4B}{\emph{Our Coding Club}, n.d.}, \textgreater).
Widespread adoption of GitHub for collaborative research tasks can ultimately enable EEB researchers to save time on creating novel processes for collaboration and focus more on their research (\protect\hyperlink{ref-ydrk01SR}{Briney et al., 2020}).
More importantly, expanding the availability of data and code management standards, of which GitHub is an increasingly important component, makes research more reproducible and collaborative (\protect\hyperlink{ref-13QX8XU3J}{Alston \& Rick, 2021}; \protect\hyperlink{ref-VDJput1V}{Gomes et al., 2022}).

@@

\leavevmode\vadjust pre{\hypertarget{ref-13jOlVcpp}{}}%
\emph{Happy Git with R}. (n.d.). Retrieved March 8, 2023, from \url{https://happygitwithr.com}

@@

\leavevmode\vadjust pre{\hypertarget{ref-nDkLlAch}{}}%
\emph{Openscapes}. (n.d.). Retrieved March 8, 2023, from \href{https:////}{//}

\leavevmode\vadjust pre{\hypertarget{ref-u5aEVE4B}{}}%
\emph{Our Coding Club}. (n.d.). Retrieved March 8, 2023, from \url{https://ourcodingclub.github.io}
